Palaeobiology demo: disparity-through-time and within groups

### 2021-07-01 inst/gitbook/08_palaeo-demo.Rmd
Added warning for data simulations in demo

>>>>

> **WARNING:** the data generated by the functions `i.need.a.matrix`, `i.need.a.tree`, `i.need.node.data` and `i.need.FADLAD` are used to **SIMULATE** data for this tutorial. This is _not_ to be used for publications or analysing real data!
> If you need a data matrix, a phylogenetic tree or FADLAD data, (`i.need.a.matrix`, `i.need.a.tree` and `i.need.FADLAD`), you will actually need to collect data from the literature or the field! If you need node data, you will need to use ancestral states estimations (e.g. using `estimate_ancestral_states` from the [`Claddis` package](https://cran.r-project.org/web/packages/Claddis/index.html)).
